Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-06 article.qmd
update

@@

@@

::: {#fig-examples .column-page layout-nrow="1"}
![](figures/examples/artemis_id_example)

![](figures/examples/stereo_id_example)

![](figures/examples/wind_id_example)

Examples of IDs from ARTEMIS, STEREO, and Wind
:::

@@

![Juno orbit](figures/juno_orbit_white){#fig-orbit}

::: {.column-page layout-nrow="1"}
![](figures/examples/artemis_id_example)

![](figures/examples/stereo_id_example)

![](figures/examples/wind_id_example)

Examples of IDs from ARTEMIS, STEREO, and Wind
:::

![Near-Earth's solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}

>>>>

::: {#fig-overview layout-ncol=1}
![](figures/juno_orbit_white){}

![](figures/juno-hg-loc_sunspot-number)

Juno orbit, its longitudinal difference with Earth & STEREO missions and sunspot number during its cruise phase

@@

![Near-Earth's and STEREO-A solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-overview}

@@

![Examples of IDs from ARTEMIS, STEREO, and Wind](figures/fig_examples){#fig-examples}

@@
